---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# mk8dx

<!-- badges: start -->

<!-- badges: end -->

The mk8dx package converts lss files for MK8DX speedruns into usable table data. It also has tools to help clean up the data.

## Installation

You can install the development version of mk8dx from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sj-io/mk8dx")
```

Load the package to your library to use it.

```{r mk8dx}
library(mk8dx)
```

## `mk_lss`

### Convert lss data to a table format

Enter a filepath into `mk_lss()` to convert .lss data into a table.

```{r mk_lss}
library(dplyr)

filepath <- "inst/extdata/bell-cup.lss"

bell_cup <- mk_lss(filepath)

head(bell_cup, 4)
```

The `mk_lss()` function reads the file as xml data using `xml2`. It then gets your file's metadata variables, attempts, and split data.

Note: All split/run times are given in seconds. If runs are not completed, the attempt time will be NA. If you reset on the first track, there will be more NA variables.

To convert a folder of lss files into one table, use `mk_lss_folder()`.

```{r}
folderpath <- "inst/extdata"

all_runs <- mk_lss_folder(folderpath)

all_runs[7:14, ]
```

## `mk_repair`
### Repair incorrectly entered data

This is an experimental function to repair some columns that might have issues if your splits were entered incorrectly, or if you have old, outdated duplicate files in the same folder as more recent data.

```{r}
repaired_runs <- mk_repair(all_runs)

repaired_runs[29:32, ]
```

Current features:

- If `individual_cup` names are entered into the `category` field, move and correct these columns.
- Trim whitespace of characters columns
- Round all attempt/split times to the hundredths place.
- Fill in missing metadata variables (only for matching category/cup)
- Update outdated split data for matching run categories/variables.

## `mk_track_names`
### Rename track names to a uniform format

The pack

This function joins the split data with
Joins with the `tracks` dataset by `category`, `individual_cup`, and `segment_id`.

```{r}
mk_track_names(repaired_runs, style = "full") %>% 
  select(category, individual_cup, segment_id, contains("segment_name")) %>% 
  distinct()
```


## `tracks` dataset

The `tracks` dataset is a list of every track in MK8DX (as of wave 4). It can be used as a reference or to standardize/correct track names for use in tables or graphs. The dataset contains the track name, in both full (`track`) and abbreviated (`trk`) forms. The original console tag (`console`) is in a separate column to allow unique styling, i.e. "(DS) Peach Gardens", "Peach Gardens DS".

```{r tracks}
tracks[13:20, ]
```

## Credits

This package is based on [Chipdelmal's MK8D package](https://github.com/Chipdelmal/MK8D), which uses python to convert lss files to a dataframe.
