---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# mk8dx

<!-- badges: start -->

<!-- badges: end -->

The mk8dx package converts lss files for MK8DX speedruns into usable table data. It also has tools to help clean up the data.

## Installation

You can install the development version of mk8dx from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sj-io/mk8dx")
```

Load the package to your library to use it.

```{r mk8dx}
library(mk8dx)
```

## `mk_lss()`: Create a table from lss data

Provide a folder or file path to `mk_lss()` to create a table from lss data.

```{r mk_lss}
library(dplyr)

bell_cup <- mk_lss("inst/extdata/bell-cup.lss")

head(bell_cup, 4)
```

The `mk_lss()` function reads the data using `xml2`. It gets the file's variables, attempts, and split data.

Note: All split/run times are given in seconds. If runs are not completed, the attempt time will be NA.

You can also provide a folder path to create one table from all lss files in the folder.

```{r}
path <- "inst/extdata"

all_runs <- mk_lss(path)

all_runs[7:14, ]
```

## `tracks` dataset

The `tracks` dataset contains every track in MK8DX (96 tracks). It can be used as a reference or to standardize/correct track names. 

Included is:

- the track name, both long (`track`) and abbreviated (`trk`)
- the original console the track appeared (`console`)
- some `id` columns to help sort/match tracks

```{r tracks}
tracks[c(15:18, 79:82), ]
```

## Credits

This package is based on [Chipdelmal's MK8D package](https://github.com/Chipdelmal/MK8D), which uses python to convert lss files to a dataframe.
